---
title: "NYC Squirrel Census"
author: "Eirik Lamøy"
date: "13 12 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
theme_set(theme_light())
```



```{r}
#library(tidytuesdayR)

nyc_squirrels <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-29/nyc_squirrels.csv")

```

Start by explore lat and long

```{r}
nyc_squirrels %>% 
  ggplot( ) +
  aes( x = long, y = lat) +
  geom_point()


by_hectar <-
  nyc_squirrels %>%
  filter( !is.na(primary_fur_color)) %>% 
  group_by(hectare) %>%
  summarise(
    long =  mean(long, na.rm = T),
    lat = mean(lat, na.rm = T),
    pct_gray = mean(primary_fur_color == "Gray", na.rm = T),
    n = n()
  )  

by_hectar %>%
  ggplot() +
  aes(long, lat, size = n) +
  geom_point() +
  theme_void()

```


```{r}
# Number of squires
nyc_squirrels %>% distinct( unique_squirrel_id) %>% count()
  
# Notes -> count 
nyc_squirrels %>% count(color_notes, sort = T)


```


```{r}
nyc_squirrels %>% 
  count( primary_fur_color, highlight_fur_color, sort = T) 


# Color of sq. differ -> 
by_hectar %>% 
  filter(n >= 10 ) %>% 
  ggplot( ) + aes( long, lat, size = n, color = pct_gray) +
  geom_point()
```



```{r}
# Number of suirrels with gray color, group by location
nyc_squirrels %>% group_by(hectare) %>% summarise( pct = sum(primary_fur_color == "Gray", na.rm =T)) %>% arrange(desc(pct))


# Viz. area by color
by_hectar %>% 
  filter( n >= 10) %>% 
  ggplot( ) + aes( lat,pct_gray) +
  geom_point() +
  geom_smooth()

```


### Logistic regression: Does the color vary by lat?
Speical trend
Spcial log. regression -> [røflig. ikke spesialområdet til DR]


```{r}

by_hectar %>% 
  mutate( n_gray = round( pct_gray*n )) %>% 
  glm( cbind(n_gray, n - n_gray) ~ lat, data = ., family = "binomial" ) %>% summary

# The higher north sq. are, more gray they 

```

squirrels may be more lukely to be gray the higher north we are in the park. And more likley to be cinnamon south.


###  
var description:
- approaches:	logical	Squirrel was seen approaching human, seeking food.
- indifferent	logical	Squirrel was indifferent to human presence.
- runs_from	logical	.Squirrel was seen running from humans, seeing them as a threat.


How is the correlation of this var-discr.?
```{r}

nyc_squirrels %>% 
  count( highlight_fur_color, sort = T)

nyc_squirrels %>% 
  count( approaches, sort = T)

nyc_squirrels %>% 
  count( approaches, indifferent ,sort = T)


```

Is a squirrel indifferent to humans?

- osb. confounding variables-> may have an affect 
```{r}
glm(  runs_from ~lat, data = nyc_squirrels,  family = "binomial") %>% summary
```


```{r}
by_hectar <-
  nyc_squirrels %>% 
  add_count( hectare) %>% 
  mutate( above_ground = !is.na(location) & location == "Above Ground") %>% 
  group_by(hectare, n) %>% 
  summarise_at( vars(long, lat, approaches:runs_from, ends_with("ing"), above_ground) , mean) %>%
  ungroup()

by_hectar %>% 
  filter( x >= 10) %>% 
  ggplot( ) + 
  aes( long, lat, size = n, color = runs_from) +
  geom_point() +
  theme_void() +
  scale_color_gradient2( low = "blue",
                        high = "red",
                        midpoint = .3,
                        labels = scales::percent ) +
  labs( color = "% of squirrels run", 
        size = "# of squirrels",
        title = "Squirrels in the northest\ncorner are more likely to run away")


```


## ggmap

```{r}
# library(ggmap)

#step 1
# get_map( location =  c(lon = -79.98, lat = 40.77))

# by_hectar %>% 
#   ggmap( ) +
#   geom_point( aes( long, lat, color = runs_from) )

```


```{r}

library( sf)

central_park_sf <- read_sf("CentralAndProspectParks")

ggplot( by_hectar) +
  geom_sf( data = central_park_sf) +
  geom_point( aes( long, lat , size = n, color = runs_from), data = by_hectar) +
  theme_void() +
    scale_color_gradient2( low = "blue",
                        high = "red",
                        midpoint = .3,
                        labels = scales::percent ) +
  labs( color = "% of squirrels run", 
        size = "# of squirrels",
        title = "Squirrels in the northest\ncorner are more likely to run away") +
  coord_sf( datum = NA)


```


## Other info from the data

What kinds of activity does the squirres do?

```{r}
# See which variables that ends with -ing
nyc_squirrels %>% select( ends_with("ing"))

nyc_squirrels %>%
  pivot_longer(names_to = "activity", values_to = "doing", ends_with("ing")) %>%
  filter( doing) %>% 
  count( activity, sort = T)
  
  
nyc_squirrels %>%
  pivot_longer(names_to = "activity", values_to = "doing", ends_with("ing")) %>%
  filter( doing) 

```


## Shiny

```{r}

next <- "next"
```



## What are the distr. of the variables.

Many of the var has median equal 0.

```{r}
by_hectar %>% 
  pivot_longer(names_to = "var", values_to = "value", approaches:foraging) %>%
  filter( n >= 10) %>% 
  ggplot() +
  aes( x = value) +
  geom_histogram() +
  facet_wrap( ~var)


```

What about include adults?

```{r}

nyc_squirrels %>% 
  count( age)

```

- not appropriate to include in the shiny-app. To many are adults


