---
title: "TidyTuesday_bobRoss"
author: "Eirik Lamøy"
date: "23 11 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse);library(janitor)

theme_set(theme_light())

```

## Bob Ross - painting by the numbers

```{r}
library(tidytuesdayR)

bob_ross <- tt_load_gh("2019-08-06")

bob_ross_data <- tidytuesdayR::tt_read_data(bob_ross, bob_ross[1]) %>% clean_names()
```

### Data cleaining

```{r}
bob_ross_elements <-
  bob_ross_data %>% 
  pivot_longer( names_to = "element", values_to = "present", apple_frame:wood_framed ) %>% 
  filter( present == 1) %>% 
  mutate( 
    title = str_remove_all(str_to_title(title), '"'), 
    element = str_to_title(str_replace(element, "_", "-"))) %>%
  select( -present) %>% 
  # !
  extract( episode, c("season", "episode_number"), "S(.*)E(.*)", remove = F , convert = T) %>% 
  arrange(season, episode_number)

```

## Look at data / Exploring the paintings

- Dont wont 2 episodes have same title:

```{r}
# Two obs. with same name: worth noting
bob_ross_elements %>% 
  count( title, sort = T)
```

What are the most commend elements?

Which title has most elements?

Number of paintings in diff. year?
```{r}
bob_ross_elements %>% 
  count(element, sort = T)

bob_ross_elements %>% 
  count(title, sort = T)

# Alternativ to count
bob_ross_elements %>% 
  group_by(season) %>% 
  summarise( n = n()) %>% arrange( desc(n))

```

Vis: Tree, Treess at the top. 
```{r}
bob_ross_gather <- bob_ross_elements

bob_ross_gather %>% 
  count(element, sort = T) %>% 
  # Adjust size
  # head( n = 15)
  head( n = 25) %>% 
  mutate( element = fct_reorder(element,n)) %>% 
  ggplot( aes( element, n) )  + 
  geom_col() +
  coord_flip()

```

What are the most crowed paintings?
```{r}
## OBS! Title are not unique

bob_ross_elements %>% 
  add_count(episode) %>% 
  arrange( desc(n))

# How many paininting did Steve Ross?

bob_ross_elements %>% filter(str_detect(element, "Steve"))

# Alternativ
# bob_ross_elements %>% 
#   count(episode, sort = T) %>%
#   head( n = 10) %>% 
#   mutate( title = fct_reorder(episode,n)) %>% 
#   ggplot( aes( title, n) )  + 
#   geom_col() +
#   coord_flip()
   
```

How have Ross`s paintings chaniged over time?

```{r}
# How many episodes each season?

bob_ross_elements %>% 
  group_by(season) %>% 
  summarise( episode = n_distinct(episode))

## Check:

bob_ross_elements %>% 
  count( episode, element, sort = T)

# Most season have tree
bob_ross_elements %>% 
  count( season, element, sort = T)

# Desided to change from percent in season to percent included diff. elements
by_season_element <-
  bob_ross_elements %>% 
  # Stopp word remove
  filter(!element %in% c("Tree", "Trees")) %>% 
  group_by( season) %>% 
  mutate( number_episodes = n_distinct(episode)) %>% 
  #add_count( season , name = "total_elements") %>% 
  #count( season, element, total_elements, sort = T) %>%
  count( season, element, number_episodes, sort = T) %>%
  # Add percent_elements
  #mutate( percent_elements = n/total_elements ) %>% 
  mutate( percent_included = n/number_episodes ) %>% 
  group_by(element) %>% 
  # To effective incl. more elements:
  mutate( element_total = sum(n)) %>% 
  ungroup()

by_season_element %>% 
  filter(element_total >= 100) %>% 
  ggplot() +
  #aes( x = season, y = percent_elements) +
  aes( x = season, y = percent_included ,color = element) +
  geom_line() +
  scale_y_continuous( labels = scales::percent_format()) +
  expand_limits( y = 0) + 
  facet_wrap(  ~element)

```

Hard to see a trend.

Lets try to use 50:

```{r}
by_season_element %>% 
  filter(element_total >= 50) %>% 
  ggplot() +
  #aes( x = season, y = percent_elements) +
  aes( x = season, y = percent_included ,color = element) +
  geom_line() +
  scale_y_continuous( labels = scales::percent_format()) +
  expand_limits( y = 0) + 
  facet_wrap(  ~element)
```

### One alternative aprproach: 
Logistic regression -> [se many models](https://r4ds.had.co.nz/many-models.html)


### Clustering 
what tends to appear together?

Using the widyr (se the vignett)

```{r}
library(widyr)

correlations <-
  bob_ross_gather %>%
  add_count( element) %>% 
  filter( n >= 5) %>% 
  pairwise_cor( element, episode, sort = T)

# Try to find a trend.
correlations %>% 
  filter(item1 == "Snow") %>% 
  mutate( item2 = fct_reorder(item2, correlation)) %>% 
  ggplot( ) +
  aes( item2, correlation) +
  geom_col() +
  coord_flip() +
  labs( title = "What tends to appear with a river", subtitle = "Among elements that appeared in at least 10 paintings")


correlations %>% 
  filter(item1 == "Structure")

correlations %>% 
  filter(item1 == "Waves")


```


### Try to by more formal

Cluster-graph

```{r}
library(ggraph)
library(igraph)

set.seed(2019)

correlations %>%
  # Number of conection:
  head( 100) %>% 
  graph_from_data_frame( ) %>% 
  ggraph( ) +
  geom_edge_link(aes(alpha = correlation)) +
  geom_node_point() +
  geom_node_text(aes(label = name ), vjust = 1, hjust = 1) +
  theme_void()

```


### Principla component Analysis (PCA)

PCA: What trend predict most about these paintings:

- Predict - What kind of painting is it? Ex. Rock palm tre->nature pictures mm.


1) What dimiensions drive a lot of the variation among paintings?
```{r}
library(reshape2)
library(broom)
binary_matrix <- bob_ross_gather %>% 
  acast( title ~ element  )


#binary_matrix %>% View()

# Center the columns

centered_matrix <- t(t(binary_matrix) - colMeans(binary_matrix))

#colSums(  binary_matrix)

svd_result <- svd(centered_matrix)


element_weights <- tidy(svd_result, matrix = "v") %>% 
  mutate( element = colnames(binary_matrix)[column])


element_weights %>% 
  # What separate tree from ocean and cloude?
  filter(PC == 2) %>% 
  top_n( 20 , abs(value)) %>% 
  mutate( element = fct_reorder(element, value)) %>% 
  ggplot( aes(element, value)) +
  geom_col() +
  coord_flip()

library(tidytext)

element_weights %>% 
  # What separate tree from ocean and cloude?
  filter(PC <= 4) %>% 
  group_by(PC) %>% 
  top_n( 16 , abs(value)) %>% 
  ungroup() %>% 
  mutate( element = reorder_within(element, value, PC)) %>% 
  ggplot( aes(element, value)) +
  geom_col() +
  facet_wrap( ~PC, scales = "free") +
  scale_x_reordered() +
  coord_flip() +
  labs( title = "First four principle components of Bob Ross paintings")

# Order of PC random. The graph shows 
# Snow vs. River/summer
# Clouds vs. Decidous
# Strong correlation, the PC is to 



```

1. Mountains vs. Ocean/Beach and decidous trees
2. Trees espacially decidous, vs Ocean
3. Summer vs. Winter
4. Lake vs. River (dont appear together)
 ( se the correlations between diff words)
 
 
What is the paiting that is stronges in painting (PC = 1) 
```{r}
# u working on rows
painting_weights <-broom::tidy(svd_result, matrix = "u") %>% 
  mutate(painting = rownames(binary_matrix)[row])
```

4 Dimention of Bobb Ross paintings
```{r}
painting_weights %>% 
  filter(PC == 1) %>% 
  arrange(desc( value ) )

# bob_ross_gather %>% 
#   filter( title == "Mountain Waterfall")

#Look at the graph facet wrapt # The positive side of the spectrum
bob_ross_gather %>% 
  filter( title == "Frozen Solitude")


painting_weights %>% 
  filter(PC == 1) %>% 
  arrange(( value ) )

#Look at the graph facet wrapt (1) The neg.end of the spectrum
bob_ross_gather %>% 
  filter( title == "Balmy Beach")


```
 

Which pictures are rel. to PC? (dim)
```{r}


painting_weights %>% 
  # What separate tree from ocean and cloude?
  filter(PC <= 4) %>% 
  group_by(PC) %>% 
  top_n( 20 , abs(value)) %>% 
  ungroup() %>% 
  mutate( element = reorder_within(painting, value, PC)) %>% 
  ggplot( aes(element, value, fill = factor(PC))) +
  geom_col(show.legend = F) +
  facet_wrap( ~PC, scales = "free") +
  scale_x_reordered() +
  coord_flip() +
  labs( title = "First four principle components of Bob Ross paintings") 
  

```

Most winter-one: Lonely retreat -> Matches PC == 3 element

### Next

Dimention that is responsible for the variation

```{r}
broom::tidy(svd_result, matrix = "d") %>% 
  ggplot( aes(PC, percent)) +
  geom_point()
```

Top five are causes the most of the variation. 
If there was no variation in the data, the curve would have been flat.


Interpre. 1 point - descr. 15% nest 11% so on..

