---
title: "pizza_rating"
author: "Eirik Lamøy"
date: "10/6/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pizza_rating

```{r}
library(tidyverse)
theme_set(theme_light())

```


[Github]https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-10-01, were the data is downloaded.

```{r import_data}
pizza_jared <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_jared.csv")
pizza_barstool <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_barstool.csv")
pizza_datafiniti <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_datafiniti.csv")

```


```{r look_at_jared}
# Five answ. per place. Multipl. quest.
pizza_jared %>% 
  count( place, question , sort = T)

# Fair: only 1, sign of messy data
pizza_jared %>% 
  count( answer , sort = T)

# Sort by time and place _ each has 5 obs
pizza_jared %>% 
  count(place, time , sort  = T)

```


Aggreage per places:
create new dataset

create a plot: What is the most pop pizza places

Se på hvordan omgjør faktorer til integer.
Dette gjør det å reordre pizza-plassene mht. factor.


```{r mutate_time}

answer_order <- c("Never Again", "Poor", "Average", "Good", "Excellent")  

by_places_answer <-
  pizza_jared %>% 
  mutate( time = as.POSIXct(time, origin = "1970-01-01"),
          date = as.Date(time)) %>% 
  # To add number to factor answer -> the fct_ need to be before group_by
  mutate(  answer = fct_relevel(answer, answer_order)) %>% 
  group_by( place, question, answer ) %>% 
  summarise( votes = sum(votes)) %>% 
  mutate( total = sum(votes)) %>% 
  mutate( percent = votes / total ) %>% 
  mutate( answer = fct_relevel(answer, answer_order),
            answer_integer = as.integer(answer) ,
            average = sum( answer_integer * percent)) %>% 
  ungroup()


# from fct_relever -> can now : fct_reorder - by average
# Places are now ordered by average rated. Prince street has the lowest. Willamsbyrg has the heighets.
by_places_answer %>% 
  filter( total > 29) %>% 
  mutate( place = fct_reorder(place, average)) %>% 
  ggplot( aes( x = answer, y =  percent) ) + 
  geom_col()+
  facet_wrap( ~ place) + 
  scale_y_continuous( labels =scales::percent ) +
  theme( axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs( y = "% of the respondents", title = "What is the most popular pizza in open stats meetup?", 
        subtitle =  "Only the 9 pizza places with respondes")

```


Trixs: Want a number to facet:
In parant is numer of answer.
```{r}

by_places_answer %>% 
  # place order by total, in descended order: filter 9
  filter( as.integer( fct_reorder( place, total, .desc = T)) <=  16 ,
          answer != "Fair") %>%   
  mutate( place = glue::glue("{ place } ({ total })"),
    place = fct_reorder(place, average)) %>% 
  ggplot( aes( x = answer, y =  percent) ) + 
  geom_col()+
  facet_wrap( ~ place) + 
  scale_y_continuous( labels =scales::percent ) +
  theme( axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs( y = "% of the respondents", title = "What is the most popular pizza in open stats meetup?", 
        subtitle =  "Only the 9 pizza places with respondes")
  
  
  
```

### Statistical test

Want to get a statical 

Weighted Lm

```{r}
library(broom)


# Lm with only the intercept
tidy(lm(c(2,4,4,5) ~1, conf.int = T))

# This doesnt work
tidy(lm(c(2,4,4,5) ~1, weights = c(1,3,10,20,15) ,conf.int = T))
  
  
t_test_repeated <- function(x, frequency) {
 tidy( t.test(rep(x, frequency)) )
}

t_test_repeated(c(1,2,3,4,5), c(100, 300, 100, 200, 150))

# Worst to best

# Alt graoh to the first (above): Good for displ. the distribution
by_places_answer %>% 
  filter(total >= 3) %>% 
  group_by(place, total) %>% 
  summarise( t_test_result = list(t_test_repeated(answer_integer, votes))) %>% 
  ungroup() %>% 
  unnest( t_test_result) %>% 
  select(place,  total ,average = estimate, low = conf.low, high = conf.high ) %>% 
  top_n(15, total) %>% 
  mutate( #place = glue::glue("{ place } ({ total })"),
          place = fct_reorder(place, average)) %>% 
  ggplot( aes( average,place)) + 
  geom_point( aes(size = total) ) +
  geom_errorbarh( aes(xmin = low, xmax = high )) +
  labs( x = "Average score (1-5) Liker scale", title = "What is the most popular pizza in open stats meetup?",
        subtitle =  "Only the 16 pizza places with the most respondents. # respond. show in parentes.", 
        size = "# Number of respondents")


# can now inner join by place
by_place <- by_places_answer %>% 
  distinct(place, total, average)
  


```


### Data set: pizza barstols
- Dont have std. Cant make a plot like above.

```{r}
# Do we have doplicate?
pizza_barstool %>%
  count(place, sort = T)

# No corr. Dont comparing them, this is a bad graph
pizza_barstool %>% 
  select( place = name,
          barstool_total = review_stats_all_count,
          barstool_average = review_stats_all_average_score) %>% 
  inner_join( by_place, by = "place") %>%
  #count( place, sort = T) # Doplicat: Joe`s Pizza. n = 3
  group_by( place) %>% 
  filter( n() == 1) %>% 
  ungroup() %>% 
  filter( barstool_total >= 5,
          total >= 5) %>% 
  ggplot( ) + 
  aes( average, barstool_average) +
  geom_point() +
  labs( x = "Meetup", y = "Barstool")
  

```


## Only look at the barstool data
 
 
```{r}
pizza_barstool %>% 
  top_n( 50, review_stats_all_count) 

pizza_barstool %>% 
  top_n( 50, review_stats_all_count) %>% 
  ggplot( ) +
  aes( price_level , review_stats_all_average_score, group = price_level) +
  geom_boxplot()
   

```
Billige er bra og dyr. De som er i mellom har lavere score.


```{r}


pizza_barstool %>% 
  filter( review_stats_all_count >= 50) %>% 
  top_n(30, review_stats_all_count) %>%
  mutate( name = fct_reorder( name,review_stats_all_average_score )) %>% 
  ggplot() +
  aes(
    review_stats_all_average_score ,
    name,
    size = review_stats_all_count
  ) + geom_boxplot() + labs(x = "Average rating", y = "", size = "# of reviews", title = "Barstool sports rating of pizza places. Only places at least 50 reviews")


```

What is the different between cities?

```{r}
pizza_barstool %>% 
  filter( review_stats_all_count >= 20) %>%
  add_count(city) %>%  
  filter( n  >= 6) %>%  
  ungroup( ) %>% 
  mutate( city = glue::glue("{ city } ({ n })")) %>% 
  ggplot( aes( city, review_stats_all_average_score)) +
  geom_boxplot() +
  labs( subtitle =  "Only pizza places with at least 20 reviews")
```



```{r}
pizza_clean <- 
  pizza_barstool %>% 
  # Denne må tas bort for scatter-plot (stage 2)
  #filter( review_stats_all_count >= 50) %>% 
  select( place = name, 
          contains("review")) %>% 
  rename_all(~str_remove(., "review_stats_")) %>% 
  select(-contains("provider") ) 

pizza_clean %>% 
  filter( critic_count > 0 ) %>% 
  # For å få en oversikt over variablene:
  # select( contains("count")) %>% 
  # gather( key, value) %>% 
  # ggplot( aes(value)) +
  # geom_histogram()+
  # facet_wrap(~ key)
  ggplot( aes(critic_average_score, dave_average_score)) +
  geom_smooth( method =  "lm", se = T) +
  # The red line indixate 1:1 from y = 0, x = 0
  geom_abline( color = "red") +
  geom_point() +
  # + coord_cartesian(xlim =  c(0, 12), ylim = c(0,12))
  labs( title = "Does Barstool sports dave agree with the critics?",
        x = "Crtical Averave score", y = "Dave score")


```


```{r}
pizza_clean %>%
  filter(community_count >= 20) %>%
  ggplot(aes(community_average_score,  dave_average_score)) +
  geom_point( aes( size = community_count)) +
  geom_abline(color = "red") +
  geom_smooth(method =  "lm") +
  labs("of community score", y = "Dave score")
  
  
```


