---
title: "Ramen rating"
author: "eal"
date: "9/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Ramen raing DavidRobinson

```{r}

library(tidyverse);
theme_set(theme_light())
ramen_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-04/ramen_ratings.csv")
```

## Look at the data

```{r}
ramen_ratings %>% 
  head() # or View()
```

first impresion:
- linear regression, predicing the star rating.

## cleaning and prepering the data

To get an understanding of which variable/factor you can get info from.


```{r}
# gather then create a barplot.
ramen_ratings %>% 
  gather(category, value,  -review_number, -stars) %>% 
  count( category, value) %>% 
  group_by( category) %>% 
  top_n( 16, n ) %>% 
  ungroup( ) %>% 
  mutate( value = fct_reorder(value, n)) %>% 
  ggplot(aes( x = value, y = n)) + 
  geom_col() + 
  facet_wrap( ~category, scale = "free_y") + 
  coord_flip()




```

variety cant be used (subset of brand?)
```{r}
# To diverse 
ramen_ratings %>% count(variety, sort = T)


```

### Lumping variables

```{r}

ramen_ratigs_processed <-   
  ramen_ratings %>% 
  # style only 4 levels
  mutate( style = fct_lump(style, n = 4)) %>%
  # remove na from style
  replace_na(list(style = "Other")) %>% 
  # Lump country. Only want 12 country
  # brand only 10 brand.
  mutate( brand = fct_lump(brand, 20), country = fct_lump(country, 12)) %>% 
  # Sett the referent level. Use other as the ref.
  mutate( brand = fct_relevel(brand, "Other"),
          country = fct_relevel(country, "Other"),
          # Relevel from Pack, sins Pack is the most command.
          style = fct_relevel(style, "Pack")) 
  


  
ramen_ratigs_processed %>% 
  gather(category, value,  -review_number, -stars) %>% 
  count( category, value) %>% 
  group_by( category) %>% 
  top_n( 16, n ) %>% 
  ungroup( ) %>% 
  mutate( value = fct_reorder(value, n)) %>% 
  ggplot(aes( x = value, y = n)) + 
  geom_col() + 
  facet_wrap( ~category, scale = "free_y") + 
  coord_flip() +
  labs( title = "categorical predictor(after prosessed)", x = "predicter", y  = "count")


```


## Linear regression

```{r}
library(broom)
lm( stars~ brand + country + style , ramen_ratigs_processed ) %>% 
  # Tidy the result from the model up, 
  # include the conf. to make the errorbars
  tidy(conf.int = T ) %>%
  filter( term != "(Intercept)") %>% 
  mutate( term = fct_reorder(term, estimate )) %>% 
  # arrange according to the estimate with the biggest impact.
  arrange(desc(estimate)) %>% 
  ggplot( aes(estimate, term ) ) + 
  geom_point() +
  geom_errorbarh( aes( xmin = conf.low, xmax = conf.high)) +
  labs(
    title = "estimated effect on ramen rating",
    x = "Estimated effect on ramen ratings",
    subtitle =  "Command brands, country and styles were lumped into Other"
  )


```



```{r}
lm( stars~ brand + country + style , ramen_ratigs_processed ) %>% 
  #
  #
  tidy(conf.int = T ) %>%
  filter( term != "(Intercept)") %>% 
  mutate( term = fct_reorder(term, estimate )) %>% 
  arrange(desc(estimate)) %>% 
  # Extract - the term text into two column:
  # The split is with a upper letter in the middel of the termword-
  extract( term, c("category", "term"),  "^([a-z]+)([A-Z].*)" ) %>% 
  mutate( term = fct_reorder(term, estimate )) %>% 
  ggplot( aes(estimate, term , color  = category) ) + 
  geom_point() +
  geom_errorbarh( aes( xmin = conf.low, xmax = conf.high)) +
  facet_wrap( ~ category, ncol = 1, scales = "free_y" ) +
  geom_vline( lty = 2, xintercept = 0) +
  theme( legend.position = "none") +
  labs(
    title = "estimated effect on ramen rating",
    x = "Estimated effect on ramen ratings",
    subtitle =  "Command brands and  country  were lumped together as the referance level. " 
  )

# Exampe interpret:
# UK vietnam does not differ to the the "Other" (which is the reference level).

```

## unnest_tokines


```{r}
library(tidytext)

ramen_ratigs_processed %>% 
  filter( !is.na(stars)) %>% 
  unnest_tokens(word, variety) %>% 
  #count(word, sort = T)
  group_by( word) %>% 
  summarise( avg_stars= mean(stars) ,
             n = n()
             ) %>% 
  arrange(desc(n))


```

 - Should have don a lasso-regression on this data.  See the wine predic. film to see lasso-regression. 

22 min.

## Web-scraping.





## Extra: rebus-quiz


```{r}
# char_class( START %R% char_class( lower( ) ) %R% char_class( upper() )%R% ANY_CHAR )
```



