---
title: "TidyTuesday Analyzing ratings and scripts from the Office"
author: "Eirik Lamøy"
date: "17 3 2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Office -

```{r}
library(tidyverse)
library(schrute)
theme_set(theme_light())
# The Office - Words and Numbers

tuesdata <- tidytuesdayR::tt_load('2020-03-17')

office_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-17/office_ratings.csv') %>%   
  mutate( name = str_to_lower(str_remove_all(title, "\\.| \\(Part.*|\\: Part.*")) )

tuesdata %>% str()

tuesdata[[1]]

```



```{r}
# Data cleaing
office_transcritps <- as_tibble(theoffice)
office_transcritps <- office_transcritps %>% 
  mutate_at(vars(index, season, episode), function(x) {as.integer(x)}) %>% 
  mutate( character = str_remove_all(character, '"') ) %>% 
    mutate( name = str_to_lower( str_remove_all(episode_name,"\\.| \\(Part.*")))




office_transcritps %>% names()

```


```{r}
office_ratings %>% 
  group_by(season) %>% 
  summarise( avg_ratings = mean(imdb_rating)) %>% 
  ggplot( aes( as.integer(season), y = avg_ratings)) +
  geom_line() +
  scale_x_continuous( breaks = 1:9)

# Organize the data
library(ggrepel)

office_ratings %>% 
  mutate( title = fct_inorder(title),
          episode_number = row_number()) %>% 
  ggplot( aes(episode_number, imdb_rating) ) +
  geom_line( ) +
  geom_smooth( se = T) +
  geom_point( aes( color = factor(season), size = total_votes )) +
   geom_text( aes(label = title), check_overlap = T, hjust = 1) +
  # Make text readble 
  expand_limits( x = -10) +
  #geom_text( aes(label = title), force = .1) +
  theme(axis.text.x = element_blank(),
        panel.grid.major.x = element_blank(),
        legend.position = "none") +
  labs( x = "Episode number", y = "IMDB ratings", title = "Popularity of the Office episodes over times", 
        subtitle = "Color rep season, size rep # of retings")
  
```


```{r}
# Most popular epiosde of the office
office_ratings %>% 
  arrange(desc(imdb_rating)) %>% 
  mutate( title = fct_reorder(title, imdb_rating)) %>% 
  head( n = 20) %>% 
  ggplot( aes(title, imdb_rating, color = factor(season) )) +
  geom_point( aes( size = total_votes)) + 
  coord_flip() +
  labs( color = "season", title = "Most pop. episodes of the office") 

```

### Transcripts

```{r}
library(tidytext)


# One line per words
blacklist <- c("yeah", "hey", "uh", "gonna")
blacklist_characer <- c("Everyone", "All", "Both", "Guy", "Girl", "Group")

transcritps_words <- 
  office_transcritps %>%
  # Number of times the character speaks
  group_by(character) %>% 
  # Only wont char. that appear more than 
  filter( n()>=100, n_distinct(episode_name) > 2) %>% 
  ungroup() %>% 
  # distinct(character) %>% count()
  select(-text_w_direction) %>% 
  unnest_tokens( word, text) %>% 
  anti_join( stop_words, by = "word") %>% 
  filter( ! word %in%  blacklist,
          ! character %in% blacklist_characer)

# Check character - for wrong cases
transcritps_words %>% count(character, sort = T)

  
transcritps_words %>%
  count(word, sort = T)
  

transcritps_words %>%
  count(character, word, sort = F)


transcritps_words %>%
  count(character, word, sort = F)
  

```


```{r}
# tf_idf -> term frequcence words, inverse words frequcency  
# What are commend for charater but not commend accrose other
# Words that are typicaly for different char.
character_td_idf <- transcritps_words %>%
  count(word, character) %>% 
  bind_tf_idf(word, character, n) %>% 
  arrange( desc(tf_idf))

character_td_idf

# What is spesific for Dwight?
character_td_idf %>%  
  #add_count(word) %>%
  filter( character %in% c("Dwight", "Jim", "Darry", "Michael", "Jan", "Hally", "David Wallace", "Holly") ) %>% 
  group_by(character) %>% 
  top_n(10, tf_idf) %>% 
  ungroup() %>% 
  mutate( word = reorder_within(word, tf_idf, character)) %>%
  ggplot( aes(word, tf_idf)) +
  geom_col() +
  coord_flip() +
  scale_x_reordered( ) +
  facet_wrap( ~character, scales = "free") +
  labs( x = "", y = "TD-IDF of character-words pairs")


```
Michael speaks much about abouat Jan, Ryan etc. 


## Machine learning model

What affectes popularity of an episode;
- Seasong/time
- Director
- Writer
- Lines per character

```{r}
# What episode name does not line up? - look at the data:
office_transcritps %>%
  count(episode_name, character) %>% 
  distinct( episode_name) %>% 
  anti_join( office_ratings, by = c(episode_name = "title"))

office_transcritps %>% 
  filter(str_detect(episode_name, "A.A.R" )  ) %>% 
  distinct( episode_name)

office_ratings %>% 
  filter(str_detect(title, "A.A.R" )  ) %>% 
  distinct( title )

# Alot of episodes does not lineup...

```

Juses a lot of time to finding out how to joining the data proper. 

Office_ratings has episodes as part 1 and 2, while transcript keep them as sep. episodes:

```{r}
# This part decided that Daivd needed to create variable name in both datasets.
# To be able to join the data propper.
office_transcritps %>%
  count(name) %>% 
  distinct( name) %>% 
  anti_join( office_ratings  , by ="name" )


office_ratings %>%
  count(name) %>% 
  distinct( name) %>% 
  anti_join( office_transcritps  , by ="name" )

## Saw that part 1 , part 2 needs to be removed..... This step -> goes up to the data again...

# Test after changing the variables
office_ratings %>%
  group_by(name) %>% 
  summarise( imbd_rating = mean(imdb_rating)) %>% 
  distinct( name) %>% 
  anti_join( office_transcritps  , by ="name" )
# could have manuelly changes the epiosdes names... on those last episodes..
```

 
- Now; do an inner_join of office_rate trans- and ratings

```{r}
ratings_summarise <- office_ratings %>% 
  group_by(name) %>% 
  summarise( imdb_rating = mean(imdb_rating))


chararcter_lines_ratings <- office_transcritps %>% 
  filter( !character %in% blacklist_characer) %>% 
  count( character, name) %>% 
  group_by(character) %>%
  # About 30 chararcter after filter 
  #filter( sum(n) >= 100) %>% 
  # COuld have different criterias:
  filter( sum(n) >= 50,
          n() >= 5) %>%
  inner_join( ratings_summarise, by = "name") 


chararcter_lines_ratings %>% 
  summarise( avg_ratings = mean(imdb_rating),
             nb_episodes = n()) %>% 
  arrange(desc(avg_ratings))

```

### control for season and other cofounding
Lasso regression model

(Chalanging: get making it correct longer, log and use of transmute (critical))

```{r}

director_writer_features <- office_transcritps %>% 
    distinct(name, director, writer) %>% 
  pivot_longer(names_to = "type", values_to =   "value", director:writer) %>% 
  separate_rows( value, sep = ";") %>% 
  # Every writer get its own line
  unite(feature, type , value,  sep = ": ") %>% 
  #add_count(feature) %>% 
  filter( n() >= 3) %>% 
  mutate( value = 1) %>% 
  ungroup()
# look at the date
# %>% 
#   count(feature, sort = T)

character_line_feature <-  chararcter_lines_ratings %>% 
  ungroup() %>% 
  #select( name , feature = character, value= (n))
  transmute( name , feature = character, value= log(n))


seasong_feature <- office_ratings %>% 
  distinct( name, season) %>% 
  transmute( name, feature = str_c("season: " ,as.character(season)), value = 1)


# Combinding them all togher
features <- bind_rows(director_writer_features,
          character_line_feature,
          seasong_feature) %>% 
    # The sparse matrix didt add up
  semi_join( office_ratings, by = "name") %>% 
  semi_join( office_transcritps, by = "name")

```


```{r}
# A sparee matrix -> term how many times char, has a line
episode_feature_matrix <-features %>% 
  cast_sparse( name, feature, value)


ratings <- ratings_summarise$imdb_rating[match(rownames(episode_feature_matrix), ratings_summarise$name)]

library(glmnet)


mod <- cv.glmnet(episode_feature_matrix, ratings)

plot(mod)

library(broom)

# Conservetive model
tidy(mod$glmnet.fit) %>% 
  filter( lambda == mod$lambda.1se,
          term != "(Intercept)") %>% 
  ggplot( aes(fct_reorder(term, estimate),  estimate, fill = estimate > 0 )) +
  geom_col() + coord_flip() +
  labs( x = "Estimate effect ")

tidy(mod$glmnet.fit) %>% 
  filter( lambda == mod$lambda.min,
          term != "(Intercept)") %>% 
  ggplot( aes(fct_reorder(term, estimate),  estimate, fill = estimate > 0 )) +
  geom_col() + coord_flip() +
  labs( x = "Estimate effect ")



```









